Clustering in a hyperbolic model of complex networks.

### 2019-05-28 proofs_infinite_k.tex
commented out the in-text-comments

\TM{ Maybe we could replace these three with a statement on $|c(k_n;G_n) - c^\ast(k_n; \Gbox)|$, at least at this point of the paper. This is only the high level description and that is all we need for the ``final proof".}\PvdH{I would vote for keeping them split, since this allows us to clearly point to the main technical challenge we have to overcome to obtain the final result.}

@@

\TM{ ``concentration'' is a loaded term in probability. I am not sure this use of the word will not be counterintuitive to many. }\PvdH{I am not sure. Concentration generally refers to how much a random variable deviates from its expectation. This is exactly what this proposition tells us. I would therefore vote for keeping this terminology, although I would have no problem with replacing it with an other term if someone has a good suggestion.}

>>>>

%\TM{ Maybe we could replace these three with a statement on $|c(k_n;G_n) - c^\ast(k_n; \Gbox)|$, at least at this point of the paper. This is only the high level description and that is all we need for the ``final proof".}\PvdH{I would vote for keeping them split, since this allows us to clearly point to the main technical challenge we have to overcome to obtain the final result.}

@@

%\TM{ ``concentration'' is a loaded term in probability. I am not sure this use of the word will not be counterintuitive to many. }\PvdH{I am not sure. Concentration generally refers to how much a random variable deviates from its expectation. This is exactly what this proposition tells us. I would therefore vote for keeping this terminology, although I would have no problem with replacing it with an other term if someone has a good suggestion.}
